---
title: "RIndividualProject_salve#1"
author: "Ben Robert T. Salve."
date: "2022-12-04"
output:
  html_document:
    df_print: paged
---

# Individual Project 1
# Ben Robert T. Salve. BSIT2-A

### Packages to be used.
### Install and load packages.
### install.packages('twitteR')
### install.packages('rtweet')
```{r}
library ('twitteR')
library ('dplyr')
library('ggplot2')
library('RColorBrewer')
library('rtweet')
library('wordcloud2')
library('tm')
```

## Set-up credentials. 
```{r}
CONSUMER_SECRET <- "l2298Ok71DCuHhfAMTypI8A88fXM03NpLV7RoV01HpS53gXdxc"
CONSUMER_KEY <- "uZQEmTPMqu0Zd15Qedgv95aW6"
ACCESS_SECRET <- "CE4k2fUjJ0zQJqHRM0Q9SkFnSK2gPbb4FnZobXRmL6HnL"
ACCESS_TOKEN <- "1595121466819084289-8XLqJsnGLYTv1xPV0m0PmC05B0v6zP"
```

## Connect to twitter.
```{r}
setup_twitter_oauth(consumer_key = CONSUMER_KEY, 
                    consumer_secret = CONSUMER_SECRET,
                    access_token = ACCESS_TOKEN,
                    access_secret = ACCESS_SECRET)
```

## Changing global options because mine has 1k limit.
```{r}
options(max.print = 10000) 
```

## Collect twitter data.
```{r}
trends <- searchTwitter("#wednesdaynetflix -filter:retweets", n = 10000, lang = "en",
                        since = "2022-11-16", until = "2022-11-30",
                        retryOnRateLimit = 120)
trends
```

## Data to data frame.
```{r}
trendsDF <- twListToDF(trends)
```

## View data.
View(trendsDF)
head(trendsDF, n= 5)
names(trendsDF)
class(trendsDF)
data_text <- head(trendsDF$text)[1:5]
data_text


## Save and load data. 
save(trendsDF,file= "trendsDF.Rdata")
save(trends, file= "trends.Rdata")
load(file= "trendsDF.Rdata")
load(file= "trends")


## Checking for missing values in a data frame.
```{r}
sapply(trendsDF, function(x) sum(is.na(x)))
```

## Subsetting.
```{r}
tweet_trends <- trendsDF %>% 
  select(screenName, text, created, statusSource)
```

## Time series.
```{r}
ts_plot(tweet_trends, "hours") +
  labs(x = NULL, y = NULL,
       title = "Frequency of tweets with a #wednesdaynetflix",
       subtitle = paste0(format(min(tweet_trends$created), "%d %B %Y"), " to ", 
                         format(max(tweet_trends$created),"%d %B %Y")),
       caption = "Data collected from Twitter's REST API via twitteR") +
  theme_classic()
```

## Time series with legend.
```{r}
ggplot(data = trendsDF, aes(x = created)) + geom_histogram(aes(fill = ..count..)) +
  xlab("Time") + ylab("Number of tweets") +
  scale_fill_gradient(low = "blue", high = "purple") +
  theme(legend.position = "left")
```

## Type of device found in source. 
```{r}
Gadgets <- function(x) {
  if(grepl(">Twitter for iPhone</a>", x)){
    "iphone"
  }else if(grepl(">Twitter for iPad</a>", x)){
    "ipad"
  }else if(grepl(">Twitter for Android</a>", x)){
    "android"
  } else if(grepl(">Twitter Web Client</a>", x)){
    "Web"
  } else if(grepl(">Twitter for Windows Phone</a>", x)){
    "windows phone"
  }else if(grepl(">dlvr.it</a>", x)){
    "dlvr.it"
  }else if(grepl(">IFTTT</a>", x)){
    "ifttt"
  }else if(grepl(">Facebook</a>", x)){  
    "facebook"
  }else {
    "others"
  }
}

trendsDF$tweetSource = sapply(trendsDF$statusSource, Gadgets)

trends_Source <- trendsDF %>% select(tweetSource) %>%
group_by(tweetSource) %>% summarize(count=n()) %>%
arrange(desc(count)) 

device_Source <- subset(trends_Source, count >10)


data_Source <- data.frame(category = trends_Source$tweetSource,
                          count = trends_Source$count)

data_Source$fraction = data_Source$count / sum(data_Source$count)
data_Source$percentage = data_Source$count / sum(data_Source$count) * 100
data_Source$ymax = cumsum(data_Source$fraction)
data_Source$ymin = c(0, head(data_Source$ymax, n=-1))
data_Source$roundP = round(data_Source$percentage, digits = 2)
```

## Type of device found in source plot. 
```{r}
Device_source <- paste(data_Source$category, data_Source$roundP, "%")
ggplot(data_Source, aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3, fill=Device_source)) +
geom_rect() + coord_polar(theta="y") + xlim(c(2, 4)) + theme_void() +
theme(legend.position = "left")
```

## Word cloud.
```{r}
screen_name <- trendsDF %>%
  select(screenName) %>%
  group_by(screenName) %>%
  summarize(count=n()) %>%
  arrange(desc(count)) 

corpus_file <- Corpus(VectorSource(trendsDF$screenName))  
class(trendsDF$screenName)

wordcloud2(data=screen_name, size=2, color='random-light',
           shape = 'star', backgroundColor="black")
```



