---
title: "RWorksheet_salve#6"
author: "Ben Robert T. Salve."
date: "2022-11-24"
output: pdf_document
---

# Worksheet 6
# Ben Robert T. Salve. BSIT2-A

## 1)
```{r}
library(ggplot2)
data(mpg)
nrow(mpg)
ncol(mpg)
```
## Answer: The number of columns in a mpg dataset is 11 while the number of rows is 234.


## 2)
## Code: 
library(dplyr)
mpg
print(mpg)
View(mpg)

most_model <- mpg %>% 
group_by(manufacturer) %>% 
tally(sort = TRUE)
most_model

most_variations <- mpg %>% 
group_by(model) %>% 
tally(sort = TRUE)
most_variations

## Output: 
## A tibble: 15 × 2
##   manufacturer     n
##   <chr>        <int>
## 1 dodge           37
## 2 toyota          34
## 3 volkswagen      27
## 4 ford            25
## 5 chevrolet       19
## 6 audi            18
## 7 hyundai         14
## 8 subaru          14
## 9 nissan          13
## 10 honda            9
## 11 jeep             8
## 12 pontiac          5
## 13 land rover       4
## 14 mercury          4
## 15 lincoln          3

## Dodge has the most models in this data set and the model that has the most variations is caravan 2wd. 


## a.
## Code: 
data1 <- mpg
u_models <- data1 %>% group_by(manufacturer, model) %>%
distinct() %>% count()
u_models
colnames(u_models) <- c("Manufacturer", "Model", "Counts")
u_models

## Output:
## A tibble: 38 × 3
## Groups:   Manufacturer, Model [38]
##   Manufacturer Model              Counts
##   <chr>        <chr>               <int>
## 1 audi         a4                      7
## 2 audi         a4 quattro              8
## 3 audi         a6 quattro              3
## 4 chevrolet    c1500 suburban 2wd      4
## 5 chevrolet    corvette                5
## 6 chevrolet    k1500 tahoe 4wd         4
## 7 chevrolet    malibu                  5
## 8 dodge        caravan 2wd             9
## 9 dodge        dakota pickup 4wd       8
## 10 dodge        durango 4wd             6
## … with 28 more rows


## b.
```{r}
qplot(model, data = mpg,geom = "bar", fill=manufacturer)
ggplot(mpg, aes(model, manufacturer)) + geom_point()
```

## 3)
## Code: 
data1 <- mpg
u_models <- data1 %>% group_by(manufacturer, model) %>%
distinct() %>% count()
u_models
colnames(u_models) <- c("Manufacturer", "Model", "Counts")
u_models

## Output:
## A tibble: 38 × 3
## Groups:   Manufacturer, Model [38]
##   Manufacturer Model              Counts
##   <chr>        <chr>               <int>
## 1 audi         a4                      7
## 2 audi         a4 quattro              8
## 3 audi         a6 quattro              3
## 4 chevrolet    c1500 suburban 2wd      4
## 5 chevrolet    corvette                5
## 6 chevrolet    k1500 tahoe 4wd         4
## 7 chevrolet    malibu                  5
## 8 dodge        caravan 2wd             9
## 9 dodge        dakota pickup 4wd       8
## 10 dodge       durango 4wd             6
## … with 28 more rows

## a.
```{r}
ggplot(mpg, aes(model, manufacturer)) + geom_point()
```
## Answer: This code shows a geometric point graph of model and manufacturer of the mpg data set. 


## b.
## Answer: For me, the plot is already useful if you want to find a specific model and what 
## manufacturer made it, then this plot can really help you find the information that you need. 


## 4)
## Code:
data2 <- u_models %>% group_by(Model) %>% count()
colnames(data2) <- c("Model","Counts")
data2

## Output:
## A tibble: 38 × 2
## Groups:   Model [38]
##   Model              Counts
##   <chr>               <int>
## 1 4runner 4wd             1
## 2 a4                      1
## 3 a4 quattro              1
## 4 a6 quattro              1
## 5 altima                  1
## 6 c1500 suburban 2wd      1
## 7 camry                   1
## 8 camry solara            1
## 9 caravan 2wd             1
## 10 civic                  1
## … with 28 more rows

## a.
```{r}
qplot(model, data= mpg, main= "Number of Cars per Model", 
      xlab= "Model", ylab= "Number of Cars", geom= "bar", fill= manufacturer) + coord_flip()
```

## b.
```{r}
data1 <- subset(mpg[c(1:20),c(1:11)])
obj_manu <- mpg$manufacturer[1:20]
obj_mode <- mpg$model[1:20]

qplot(obj_mode, data = data1, main = "Number of Cars per Model", 
      xlab = "Model",ylab = "Number of Cars", geom = "bar", fill = obj_manu) + coord_flip()
```

## 5)
## a.
```{r}
ggplot(data = mpg , mapping = aes(x = displ, 
  y = cyl, main = "Relationship between No. of Cylinders and Engine Displacement")) + 
  geom_point(mapping=aes(colour = "engine displacement")) 
```

## b.
## Answer: In the y axis we have the number of cylinders and in the x axis we have the displacement,
## the red dots represents the engine displacement. The plot is about the ctlinders by displacement. 


## 6)
## a.
```{r}
ggplot(data= mpg, mapping= aes(x= drv, y= class)) + 
  geom_point(mapping= aes(color= class)) + geom_tile()
```                                                                                     

## b.
## Answer: It is class by the type of drive train, where f = front-wheel drive, 
## r = rear wheel drive, 4 = 4wd. The plot looks like a heatmap but the color is black.
## The class or the legend has color representations but the plot doesn't have any color. 



## 7)
## Code 1.
```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, colour = "blue"))
```

## Code 2.
```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy), colour = "blue")
```

## Answer: The difference between code 1 and code 2 is that in code 1 colour is for 
## representing what the dot is. It is basically a legend, while in code 2 it is 
## for changing the color of the dots.


## 8)
```{r}
?mpg
```

## Answer: The result of the command is that it opened up the help tab. It gave the title 
## Fuel economy data from 1999 to 2008 for 38 popular models of cars, it gave a short description,
## usage, and format.


## a.
## Answer: The variables that are categorical in the mpg data set are
## manufacturer, model, trans, drv, fl, and class.


## b.
## Answer: The continuous variables in the mpg data set are displ, year, cyl.


## c.
```{r}
ggplot(mpg, aes(x = displ, y = hwy, colour = cty)) + geom_point()
```
## Answer: The plot is keeping track of the cty by having different hues of color blue.
## It produced this output because of the ggplot code. 


## 9)
```{r}
ggplot(data= mpg, mapping = aes(x= displ, y= hwy)) + geom_point(mapping= aes(color= class)) +
  geom_smooth(se= FALSE)
```

## 10)
```{r}
ggplot(data= mpg, mapping= aes(x= displ, y= hwy, color= class)) + geom_point() +
  geom_smooth(se= FALSE)
```
