---
title: "RWorksheet_salve#7"
author: "Ben Robert T. Salve."
date: "2022-12-10"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

# Worksheet 7
# Ben Robert T. Salve. BSIT2-A

## 1)
```{r}
Student<- seq(1:10)
Pre_Test<- c(55, 54, 47, 57, 51, 61, 57, 54, 63, 58)
Post_Test<- c(61, 60, 56, 63, 56, 63, 59, 56, 62, 61)

df1 <- data.frame(Student, Pre_Test, Post_Test)
df1
```
## a.
```{r}
library(Hmisc)
library(pastecs)

describe(df1)
stat.desc(df1)
```

## 2)
```{r}
data1<- c(10, 10, 10, 20, 20, 50, 10, 20, 10, 50, 20, 50, 20, 10)
data1
```
## a.
```{r}
factored_data<- factor(data1, ordered = TRUE)
factored_data
```
## Answer: The output of the code displayed the levels of the factored_data object which are 
## 10 is less than 20 and 20 is less than 50.


## 3) 
```{r}
subjects<- c("l", "n", "n", "i", "l", "l", "n", "n", "i", "l")
```
## a.
```{r}
represent<- data.frame(subjects)
represent
```
## Answer: The best way to represent this data in R is to make a data frame. 


## 4)
```{r}
sample_accountants<- c("tas", "sa", "qld", "nsw", "nsw", "nt", "wa", "wa", "qld", "vic", "nsw", 
                        "vic", "qld", "qld", "sa", "tas", "sa", "nt", "wa", "vic", "qld", "nsw",
                        "nsw", "wa", "sa", "act", "nsw", "vic", "vic", "act")
sample_accountants
```
## a.
```{r}
factored_sample_accountants<- factor(sample_accountants)
factored_sample_accountants

a4<- levels(factored_sample_accountants)
a4
```
## Answer: The factor function displays everything inside the combine and displays the level,
## it displayed the elements without repeating it. While the factor level it just displayed 
## the levels.


## 5)
```{r}
incomes<- c(60, 49, 40, 61, 64, 60, 59, 54, 62, 69, 70, 42, 56, 61, 61,
             61, 58, 51, 48, 65, 49, 49, 41, 48, 52, 46, 59, 46, 58, 43)
incomes
```
## a.
```{r}
income_apply<- tapply(incomes, sample_accountants, mean)
income_apply 
```
## b.
```{r}
income_apply 
```
## Answer: It displayed the mean of the income for each sample_accountants. 


## 6)
```{r}
stdError <- function(x) sqrt(var(x)/length(x))
```
## a.
## Answer: The standard error describes the variation between the calculated mean of 
## the population and one which is considered known, or accepted as accurate.
```{r}
std_error_n<- length(income_apply)
std_error_sd<- sd(income_apply)
std_error_se<- std_error_sd/sqrt(std_error_n)
std_error_se
```
## b.
## Answer: By dividing the sd(), sqrt(), or length() you will get the standard errors as result. 

## 7)
```{r}
data(Titanic)
#View(Titanic)
titanic_dataset<- data.frame(Titanic)
```
## a.
```{r}
survived<- subset(titanic_dataset, Survived == "Yes")
survived

did_not_survived<- subset(titanic_dataset, Survived == "No")
did_not_survived
```

## 8)
## a.
## Answer: The data sets pertain to Wisconsin's breast cancer. Periodically as Dr. Wolberg 
## discusses his clinical cases, samples start to come. This chronological grouping of the 
## data is therefore reflected in the database.

## b.
library(readxl)
getwd()
Breast_Cancer<- read_excel("Breast_Cancer.xlsx")
View(Breast_Cancer)

## c.
## c1.
## Code: 
c1_n <- length(Breast_Cancer$`CL. thickness`)
c1_sd <- sd(Breast_Cancer$`CL. thickness`)
c1_se <- c1_sd/sqrt(Breast_Cancer$`CL. thickness`)
c1_se
## Output:
## [1] 1.2812754 1.2812754 1.6541194 1.1696391 1.4325095 1.0129371 2.8650189 2.0258743 2.0258743 1.4325095
## [11] 2.8650189 2.0258743 1.2812754 2.8650189 1.0129371 1.0828754 1.4325095 1.4325095 0.9059985 1.1696391
## [21] 1.0828754 0.9059985 1.6541194 1.0129371 2.8650189 1.2812754 1.6541194 1.2812754 2.0258743 2.8650189
## [31] 1.6541194 2.0258743 0.9059985 2.0258743 1.6541194 2.0258743 0.9059985 1.1696391 1.2812754 2.0258743
## [41] 1.1696391 0.9059985 1.1696391 1.2812754 0.9059985 2.8650189 1.6541194 2.8650189 1.4325095

## c2.
## Code:
c2<- sd(Breast_Cancer$`Marg. Adhesion`) / mean(Breast_Cancer$`Marg. Adhesion`) * 100
c2
## Output:
## [1] 97.67235

## c3.
## Code:
c3 <- subset(Breast_Cancer,`Bare. Nuclei` == "NA")
c3
## Output:
##  A tibble: 2 × 11
##  Id `CL. thickness` `Cell size` `Cell Shape` Marg. A…¹ Epith…² Bare.…³ Bl. C…⁴ Norma…⁵ Mitoses Class
##  <dbl>           <dbl>       <dbl>        <dbl>     <dbl>   <dbl> <chr>     <dbl>   <dbl>   <dbl> <chr>
##   1 1057013               8           4            5         1       2 NA            7       3       1 mali…
##  2 1096800               6           6            6         9       6 NA            7       8       1 beni…
##  … with abbreviated variable names ¹​`Marg. Adhesion`, ²​`Epith. C.size`, ³​`Bare. Nuclei`,
##    ⁴​`Bl. Cromatin`, ⁵​`Normal nucleoli`

## c4.
## Code:
c4<- mean(Breast_Cancer$`Bl. Cromatin`)
c4.1<- sd(Breast_Cancer$`Bl. Cromatin`)
c4
## Output:
## [1] 3.836735

c4.1
## Output:
## [1] 2.085135

## c5.
## Mean.
## Code:
c5 <- mean(Breast_Cancer$`Cell Shape`)
c5
## Output:
## [1] 3.163265

## Standard error of the mean.
## Code:
c5.1 <- length(Breast_Cancer$`Cell Shape`)
c5.2 <- sd(Breast_Cancer$`Cell Shape`)
c5.3 <- c5.2/sqrt(c5.1)
c5.3
## Output:
## [1] 0.4158294

## Finding the t-score that corresponds to the confidence level.
## Code:
c5.4 = 0.05
c5.5 = c5.1 - 1
c5.6 = qt(p= c5.4/2, df= c5.5, lower.tail= F)
c5.6
## Output:
## [1] 2.010635

## Constructing the confidence interval.
## Code:
c5.7 <- c5.6* c5.3
c5.7 
## Output:
## [1] 0.836081

## Lower.
## Code:
c5.8 <- c5 - c5.7
c5.8
## Output:
## [1] 2.327184

## Upper.
## Code:
c5.9 <- c5 + c5.7

c(c5.8, c5.9)
## Output:
## [1] 2.327184 3.999346

## d.
## Code:
attributes(Breast_Cancer)
## Output:
## $names
## [1] "Id"              "CL. thickness"   "Cell size"       "Cell Shape"      "Marg. Adhesion" 
## [6] "Epith. C.size"   "Bare. Nuclei"    "Bl. Cromatin"    "Normal nucleoli" "Mitoses"        
## [11] "Class"          

## e.
## Code:
e8 <- subset(Breast_Cancer, Class == "malignant")
e8
## Output:
##  A tibble: 1 × 11
##  Id `CL. thickness` `Cell size` `Cell Shape` Marg. A…¹ Epith…² Bare.…³ Bl. C…⁴ Norma…⁵ Mitoses Class
##  <dbl>           <dbl>       <dbl>        <dbl>     <dbl>   <dbl> <chr>     <dbl>   <dbl>   <dbl> <chr>
##   1 1017122               8          10           10         8       7 10            9       7       1 mali…
##  … with abbreviated variable names ¹​`Marg. Adhesion`, ²​`Epith. C.size`, ³​`Bare. Nuclei`,
##    ⁴​`Bl. Cromatin`, ⁵​`Normal nucleoli`

## Percentage.
## Code:
17  / 49 * 100
## Output:
## [1] 34.69388

## Answer: There are 17 respondents who are malignant and 49 respondents. The result 
## is that 34.69388 or 35% of respondents are malignant.


## 9.
## install.packages('AppliedPredictiveModeling')
library("AppliedPredictiveModeling")
data(abalone)
View(abalone)
head(abalone)
summary(abalone)

## install.packages('xlsx')
library(xlsx)
write.xlsx(abalone,"/Users/miasalve/Desktop/Home folder/ISAT-U files/BSIT 2-A/abalone.xlsx")

